When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-29 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote about BIC/AIC and stop rules

An exploratory ANOVA was used to compare the fit of the final model with a linear random intercept model, confirming that the two models were different from each other ($\chi^2 (`r compare_h2b$Df[2]`)$ = `r compare_h2b$Chisq[2]`, $p<.001$), and with an Akaike Information Criterion of $AIC=`r compare_h2b$AIC[2]`$ and a Bayesian Information Criterion of $BIC=`r compare_h2b$BIC[2]`$ the declining logistic model was superior to the linear model ($AIC=`r compare_h2b$AIC[1]`$, $BIC=`r compare_h2b$BIC[1]`$).
The final model had an effect size of $f^{2}=$ `r round(h2b_level_f2, digits = 2)` for the $n$-back levels and $f^{2}=$ `r round(h2b_dprime_f2, digits = 2)` for $d'$, which are considered large and small, respectively [@Cohen1992].
This means that the $n$-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and $d'$ explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
The beta coefficient indicated that with every 1-unit increase in $d'$, the SV increased by `r as.numeric(h2b_result.table[3,"Beta"])`.
Due to the coding scheme of the logistic contrast, the beta coefficient of the $n$-back level has to be interpreted inversely, so SVs decline with increasing $n$-back level.
The effect size of the median RT was $f^{2}=$ `r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.
Since SVs decline with increasing level, beyond the variance explained by $d'$, evidence was in favour of H2b.

@@

When developing a new paradigm, it is challenging to decide on the optimal analysis strategy, as every hypothesis is based on expected data patterns rather than previous findings.
While the Stage 1 review process made the analyses as robust as possible, there were still unknown factors that should be addressed by future studies.
For instance, the differences between participants with higher and lower NFC should be investigated with extreme groups rather than a median split, or even more promising, as a continuous measure, especially in academic samples where NFC can be expected to be higher on average and more narrow in range.
Additionally, we expected the SVs of participants with lower NFC scores to peak at 1-back and the SVs of those with higher scores to peak at 2-back, but the way the SVs of both groups appeared to drift apart in the higher $n$-back levels suggests that an analysis of those levels would be more fruitful in determining group differences.
Future studies could create a stronger separation between the concepts investigated in this study (discounting curve, effort perception, performance, SV computation, NFC), and model the SVs and their task-related influencing factors first, before looking at (non-linear) associations with personality.
Another important point is the instruction, not just for the $n$-back task, but for the effort discounting as well.
We had to exclude several participants for misunderstanding the task instruction, so we will add a visual instruction or a training next time.
And even though the participants were instructed to do the effort discounting with the aim to be satisfied with their choices instead of trying to increase the rewards, we cannot be sure that they did so.
One might also argue that the 2€ reward range was not large enough to be an incentive for effort expenditure.
However, findings by Bialaszek et al.[-@Bialaszek2017] suggest that participants are actually more sensitive to effort when the reward is small.
Nevertheless, we exceeded the largest required sample size by `r round(nrow(data_quest)/53, digits = 1)` times, which gives our analyses high statistical power.

>>>>

An exploratory ANOVA was used to compare the fit of the final model with a linear random intercept model, confirming that the two models were different from each other ($\chi^2 (`r compare_h2b$Df[2]`)$ = `r compare_h2b$Chisq[2]`, $p<.001$), and with an Akaike Information Criterion of $AIC=`r compare_h2b$AIC[2]`$ and a Bayesian Information Criterion of $BIC=`r compare_h2b$BIC[2]`$ the declining logistic model was superior to the linear model ($AIC=`r compare_h2b$AIC[1]`$, $BIC=`r compare_h2b$BIC[1]`$).
Both AIC and BIC subtract the likelihood of the model from the number of parameters and/or data points, so lower values indicate better model fit.
The final model had an effect size of $f^{2}=$ `r round(h2b_level_f2, digits = 2)` for the $n$-back levels and $f^{2}=$ `r round(h2b_dprime_f2, digits = 2)` for $d'$, which are considered large and small, respectively [@Cohen1992].
This means that the $n$-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and $d'$ explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
The beta coefficient indicated that with every 1-unit increase in $d'$, the SV increased by `r as.numeric(h2b_result.table[3,"Beta"])`.
Due to the coding scheme of the logistic contrast, the beta coefficient of the $n$-back level has to be interpreted inversely, so SVs decline with increasing $n$-back level.
The effect size of the median RT was $f^{2}=$ `r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.
Since SVs decline with increasing level, beyond the variance explained by $d'$, evidence was in favour of H2b.

@@

When developing a new paradigm, it is challenging to decide on the optimal analysis strategy, as every hypothesis is based on expected data patterns rather than previous findings.
While the Stage 1 review process made the analyses as robust as possible, there were still unknown factors that should be addressed by future studies.
For instance, the differences between participants with higher and lower NFC should be investigated with extreme groups rather than a median split, or even more promising, as a continuous measure, especially in academic samples where NFC can be expected to be higher on average and more narrow in range.
To arrive at a sample with more balanced NFC scores, recruitment efforts should be focused on representative population samples and/or collecting data with an NFC-based stop rule.
Additionally, we expected the SVs of participants with lower NFC scores to peak at 1-back and the SVs of those with higher scores to peak at 2-back, but the way the SVs of both groups appeared to drift apart in the higher $n$-back levels suggests that an analysis of those levels would be more fruitful in determining group differences.
Future studies could create a stronger separation between the concepts investigated in this study (discounting curve, effort perception, performance, SV computation, NFC), and model the SVs and their task-related influencing factors first, before looking at (non-linear) associations with personality.
Another important point is the instruction, not just for the $n$-back task, but for the effort discounting as well.
We had to exclude several participants for misunderstanding the task instruction, so we will add a visual instruction or a training next time.
And even though the participants were instructed to do the effort discounting with the aim to be satisfied with their choices instead of trying to increase the rewards, we cannot be sure that they did so.
One might also argue that the 2€ reward range was not large enough to be an incentive for effort expenditure.
However, findings by Bialaszek et al.[-@Bialaszek2017] suggest that participants are actually more sensitive to effort when the reward is small.
Nevertheless, we exceeded the largest required sample size by `r round(nrow(data_quest)/53, digits = 1)` times, which gives our analyses high statistical power.
